---
title: "Final"
author: "Anna Truong"
date: "4/25/2017"
output: html_document
---

#Install Package
```{r}
library(glmnet)
library(tm)
library(SnowballC)
library(factoextra)
library(randomForest)
library(caret)
library(corrplot)
library(plyr)
data("crude")
```


#Import Data
```{r}
user <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_user.csv")[,-1]
review_train_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_review_train.csv")[,-1]
review_test_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_review_test.csv")[,-1]
business_train_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_business_train.csv")[,-1]
business_test_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_business_test.csv")[,-1]

train_word <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Re-try/train_word.csv")
test_word <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Re-try/test_word.csv")
ncol(train_word)
ncol(test_word)

review_train <- review_train_ori[,names(review_train_ori)%in% c("funny","user_id","text","business_id","stars","useful","cool")]
colnames(review_train) <- c("funny_review","user_id","text","business_id","stars_review", "useful_review","cool_review")

review_test <- review_test_ori[ ,names(review_test_ori)%in% c("funny","user_id","text","business_id","useful","cool")]
colnames(review_test) <- c("funny_review","user_id","text","business_id","useful_review","cool_review")


business_test <- business_test_ori[, names(business_test_ori)%in%c("business_id","is_open","city","review_count")]
colnames(business_test) <- c("business_id","is_open","city","review_count_business")

business_train <- business_train_ori[, names(business_train_ori)%in%c("business_id","is_open","city","review_count")]
colnames(business_train) <- c("business_id","is_open","city","review_count_business")
```

#Train Test Dataset
```{r}
#TRAIN
train.bybusiness <- merge(review_train,business_train,by="business_id")
train.byuser <- merge(train.bybusiness,user,by="user_id")
train <- train.byuser[,names(train.byuser)%in% c("business_id","funny_review","stars_review","useful_review","cool_review","is_open","city","review_count_business","useful","compliment_photos","compliment_list","compliment_funny","compliment_plain","review_count","fans","compliment_not","funny","compliment_writer","compliment_cute","average_stars","compliment_more","friends","compliment_hot","cool","compliment_profile","compliment_cool")]

#count number of friends they have
friends_list = strsplit(as.character(train$friends), ",")
num_friends = c()

for (i in 1:length(friends_list)) {
  num_friends[i] = length(friends_list[[i]])
}
friends = num_friends

city.f <- factor(train$city)
city <- model.matrix(~city.f)[,-1]
ncol(city)

train.aggr <- data.frame(train[,!(names(train)%in%c("city","friends"))],friends,city,train_word)



#TEST
test.bybusiness <- merge(review_test,business_test,by="business_id")
test.byuser <- merge(test.bybusiness,user,by="user_id")
test <- test.byuser[,names(test.byuser)%in% c("business_id","funny_review","stars_review","useful_review","cool_review","is_open","city","review_count_business","useful","compliment_photos","compliment_list","compliment_funny","compliment_plain","review_count","fans","compliment_not","funny","compliment_writer","compliment_cute","average_stars","compliment_more","friends","compliment_hot","cool","compliment_profile","compliment_cool")]


#count number of friends they have
friends_list = strsplit(as.character(test$friends), ",")
num_friends = c()

for (i in 1:length(friends_list)) {
  num_friends[i] = length(friends_list[[i]])
}
friends = num_friends

city.f <- factor(test$city)
city <- model.matrix(~city.f)[,-1]
ncol(city)

test.aggr <- data.frame(test[,!(names(test)%in%c("city","friends"))],friends,city,test_word)
ncol(test_word)
ncol(train_word)
ncol(test)
ncol(train)
ncol(test.aggr)
ncol(train.aggr)
colnames(train.aggr[,-1])

```

##Aggregate Train and Test
```{r}
train.aggr.mean <- aggregate(train.aggr[,-1], by=list(train.aggr$business_id), mean) 

test.aggr.mean <- aggregate(test.aggr[,-1], by=list(test.aggr$business_id), mean) 


train_word.mean <- train.aggr.mean[,c(which(colnames(train.aggr.mean)=="abl"):ncol(train.aggr.mean))]
test_word.mean <- test.aggr.mean[,c(which(colnames(test.aggr.mean)=="abl"):ncol(test.aggr.mean))]

```

##Set Seed
```{r}
set.seed(227)
```


##Reduce Dimensionality of Text with PCA
```{r}
train_word.pca <- prcomp(train_word.mean, center=TRUE, scale=TRUE)
eig.val <- get_eigenvalue(train_word.pca)
text_reduced <- train
eig.val[which(eig.val$cumulative.variance.percent>97)[1],]
text.reduced_train <- train_word.pca$x[,c(1:which(eig.val$cumulative.variance.percent>97)[1])] 
dim(text.reduced_train)
nrow(train.aggr.mean)
```

##Construct X and y for train
```{r}
#Construct y
y.train <- train.aggr.mean$stars_review 

#Construct X
train.aggr.mean.nostar.nobusinessid <- train.aggr.mean[,!(names(train.aggr.mean)%in%c("stars_review","Group.1"))]

X.train<- as.matrix(data.frame(train.aggr.mean.nostar.nobusinessid[,-c(which(colnames(train.aggr.mean.nostar.nobusinessid)=="abl"):ncol(train.aggr.mean.nostar.nobusinessid))],text.reduced_train))

```


##Lasso Model 
```{r}
lasso_train <- cv.glmnet(x=X.train,y=y.train,alpha=1)
penalty.lasso <- lasso_train$lambda.min
lasso_train.best <- glmnet(x=X.train,y=y.train,alpha=1,lambda=penalty.lasso)
coef(lasso_train.best)
```

##Check Model Lasso
```{r}
ypred_train <- predict(lasso_train.best, newx=X.train)
rmse_lasso <- sqrt(mean((ypred_train-y.train)^2))
rmse_lasso
```


##Ridge Model 
```{r}
ridge_train <- cv.glmnet(x=X.train,y=y.train,alpha=0)
penalty.ridge <- ridge_train$lambda.min
ridge_train.best <- glmnet(x=X.train,y=y.train,alpha=0,lambda=penalty.ridge)
coef(ridge_train.best)
```

##Check Model Ridge
```{r}
ypred_train <- predict(ridge_train.best, newx=X.train)
rmse_ridge <- sqrt(mean((ypred_train-y.train)^2))
rmse_ridge
```



##Construct X and y in Test
```{r}
PCA_test <- predict(train_word.pca, newdata=test_word.mean)

text.reduced_test <- PCA_test[,c(1:which(eig.val$cumulative.variance.percent>97)[1])]

#Construct X
test.aggr.mean.nostar.nobusinessid <- test.aggr.mean[,!(names(test.aggr.mean)%in%c("stars_review","Group.1"))]

X.test<- as.matrix(data.frame(test.aggr.mean.nostar.nobusinessid[,-c(which(colnames(test.aggr.mean.nostar.nobusinessid)=="abl"):ncol(test.aggr.mean.nostar.nobusinessid))],text.reduced_test))

```




##Predict Test Lasso 
```{r}
y.test <- predict(lasso_train.best, newx=X.test)
predict.lasso_test <- data.frame(test.aggr.mean[,1],y.test)
colnames(predict.lasso_test) <- c("business_id","stars")
write.csv(predict.lasso_test, "lasso_aggregate.csv",row.names = FALSE)
```



##Predict on Test Ridge 
```{r}
y.test <- predict(ridge_train.best, newx=X.test,, predict.all=FALSE)
predict.ridge_test <- data.frame(test.aggr.mean[,1],y.test)
colnames(predict.ridge_test ) <- c("business_id","stars")
write.csv(predict.ridge_test, "ridge_aggregate.csv",row.names = FALSE)
```


##Random Forest Model 
```{r}
train_rf <- data.frame(y.train,X.train)
rf_train <- randomForest(y.train~., data=train_rf)
which.min(rf_train$mse)
rf_train.best <- randomForest(y.train~., data=train_rf,ntree=which.min(rf_train$mse))

```

##Check Model RF
```{r}
ypred_train <- predict(rf_train.best, newx=X.train)
rmse_rf <- sqrt(mean((ypred_train-y.train)^2))
rmse_rf
```

##Predict on Test RF not cleaned
```{r}
y.test <- predict(rf_train.best, newdata=X.test)
predict.rf_test <- data.frame(test.aggr.mean[,1],y.test)
colnames(predict.rf_test) <- c("business_id","stars")
write.csv(predict.rf_test, "rf_aggregate.csv",row.names = FALSE)
```



#Extra Data Cleaning
```{r}
#Construct train data
train.dt <- data.frame(y.train, X.train)

# Remove Zero and Near Zero-Variance Predictors
nzv <- nearZeroVar(train.dt)
nzv

# Calculate correlation matrix
descrCor <- cor(train.dt)
print(descrCor) # Print correlation matrix
summary(descrCor[upper.tri(descrCor)])

# find attributes that are highly corrected
highlyCorrelated <- findCorrelation(descrCor, cutoff=0.9)
highlyCorrelated 
highlyCorCol <- colnames(train.dt)[highlyCorrelated]

# Remove highly correlated variables and create a new dataset
train.dt_clean <- train.dt[, -which(colnames(train.dt) %in% highlyCorCol)]
dim(train.dt_clean)

#Train Random Forest
rf <-randomForest(y.train~.,data=train.dt_clean, importance=TRUE,ntree=1000)

#Evaluate variable importance
imp = importance(rf, type=1)
imp <- data.frame(predictors=rownames(imp),imp)

# Order the predictor levels by importance
imp.sort <- arrange(imp,desc(imp$X.IncMSE))
imp.sort$predictors <- factor(imp.sort$predictors,levels=imp.sort$predictors)

# Select the top  predictors
imp.top <- imp.sort[1:599,]

# Subset data with 599 independent and 1 dependent variables
train.clean = cbind(stars = train.dt_clean$y.train, train.dt_clean[, as.character(imp.top$predictors)])


```



```{r}
X_cleantest <- X.test[,as.character(imp.top$predictors)]
train.clean <- data.frame(y.train, X_cleantest)
```


##Lasso Model on cleaned train
```{r}
set.seed(50)
lasso_cleantrain <- cv.glmnet(x=as.matrix(train.clean[,-1]),y=train.clean$stars,alpha=1)
penalty.cleanlasso <- lasso_cleantrain$lambda.min
lasso_cleantrain.best <- glmnet(x=as.matrix(train.clean[,-1]),y=train.clean$stars,alpha=1,lambda=penalty.cleanlasso)
coef(lasso_cleantrain.best)
y.train_pred <- predict(lasso_cleantrain.best, newx = as.matrix(train.clean[,-1]))
sqrt(mean((y.train-y.train_pred)^2))
```

##ridge Model on cleaned train
```{r}
set.seed(50)
ridge_cleantrain <- cv.glmnet(x=as.matrix(train.clean[,-1]),y=train.clean$stars,alpha=1)
penalty.cleanridge <- ridge_cleantrain$lambda.min
ridge_cleantrain.best <- glmnet(x=as.matrix(train.clean[,-1]),y=train.clean$stars,alpha=1,lambda=penalty.cleanridge)
coef(ridge_cleantrain.best)
y.train_pred <- predict(ridge_cleantrain.best, newx = as.matrix(train.clean[,-1]))
sqrt(mean((y.train-y.train_pred)^2))
```
