---
title: "Final"
author: "Anna Truong"
date: "4/25/2017"
output: html_document
---

#Install Package
```{r}
library(lubridate)
library(randomForest)
library(glmnet)
library(tm)
library(SnowballC)
library(factoextra)
library(caret)
library(corrplot)
library(plyr)
data("crude")
```


#Import Data
```{r}
user_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_user.csv")[,-1]
review_train_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_review_train.csv")[,-1]
review_test_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_review_test.csv")[,-1]
business_train_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_business_train.csv")[,-1]
business_test_ori <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Data/yelp_academic_dataset_business_test.csv")[,-1]

```

##Choose useful columns
```{r}
business_train <- business_train_ori[, names(business_train_ori)%in%c("business_id","is_open","city","review_count")]

business_test <- business_test_ori[,names(business_test_ori)%in%c("business_id","is_open","city","review_count")]

review_train <- review_train_ori[,names(review_train_ori)%in%c("funny","user_id","text","business_id","stars","date","useful","cool")]
colnames(review_train) <- c("funny_review","user_id","text","business_id","stars","date","useful_review","cool_review")

review_test <- review_test_ori[,names(review_test_ori)%in%c("funny","user_id","text","business_id","date","useful","cool")]
colnames(review_test) <- c("funny_review","user_id","text","business_id","date","useful_review","cool_review")

user <- user_ori[,!(names(user_ori)%in%c("yelping_since","elite","type","name"))]
```

##Modify Users
```{r}
friends_list = strsplit(as.character(user$friends), ",")

num_friends = c()
for (i in 1:length(friends_list)) {
  num_friends[i] = length(friends_list[[i]])
}
user$friends = num_friends
```

#Train Test Dataset
```{r}
train.bybusiness <- merge(review_train,business_train,by="business_id")
train.byuser <- merge(train.bybusiness,user,by="user_id")
train <- train.byuser[,-c(1:2)]

test.bybusiness <- merge(review_test, business_test, by="business_id")
test.byuser <- merge(test.bybusiness,user,by="user_id")
test <- test.byuser[,-c(1:2)]
```


##Wordbank Construction
```{r}
#Clean text in train
text.low_train <- tolower(train$text)
text_train <- gsub("[^![:^punct:]]", "", text.low_train, perl=T)
train$text <- gsub('[[:digit:]]+', '', text_train)

#Clean text in test
text.low_test <- tolower(test$text)
text_test <- gsub("[^![:^punct:]]", "", text.low_test, perl=T)
test$text <- gsub('[[:digit:]]+', '', text_test)


wordbank.original <- c(unlist(strsplit(test$text, " "), recursive=FALSE),unlist(strsplit(train$text, " "), recursive=FALSE))


stopwords <- c('i', 'ive','me', 'my', 'myself', 'we', 'our', 'ours', 'ourselves', 'you', 'your', 'yours', 'yourself', 'yourselves', 'he','hes','youre','u','ur','shes','theyre','shes','isnt','arent','im','wont','shouldnt','doesnt','dont','didnt','hasnt','havent','him', 'his', 'himself', 'she', 'her', 'hers','herself', 'it','ill','itll','shell','theyll', 'its', 'itself', 'they', 'them', 'their', 'theirs', 'themselves','what', 'which', 'who', 'whom', 'this', 'that','where','when','why','how', 'these', 'those', 'am', 'is', 'are','was', 'were', 'be', 'been', 'being', 'have', 'has', 'had', 'having', 'do', 'does','did', 'doing', 'a', 'an', 'the', 'and', 'but', 'if', 'or', 'because', 'as', 'until','while', 'of', 'at', 'by', 'for', 'with', 'about', 'against', 'between', 'into','through', 'during', 'before', 'after', 'above', 'below', 'to', 'from', 'up', 'down','in', 'out', 'on', 'off', 'over', 'under', 'again', 'further', 'then', 'once', 'here','there', 'when', 'where', 'why', 'how', 'all', 'any', 'both', 'each', 'few', 'more','most', 'other', 'some', 'such', 'no', 'nor', 'not', 'only', 'own', 'same', 'so','than', 'too', 'very', 's', 't', 'can', 'will', 'just', 'don', 'should', 'now','may','0','1','2','3','4','5','6','7','8','9','10', '')


wordbank <- unname(wordbank.original[!wordbank.original%in%stopwords])
wordbank <- wordStem(wordbank, language = "porter")
wordbank <- names(table(wordbank)[table(wordbank)/length(wordbank)>.0001])
wordbank <- wordbank[17:length(wordbank)]
length(wordbank)

write.csv(wordbank,"wordbank.csv",row.names = FALSE)
length(wordbank)
```

#Function to clean text
```{r}
split <- function(vector) strsplit(vector," ") #split text
clean.tokens <- function(vector) vector[!(vector %in% stopwords)] #eliminate stopwords
tokens.stem <- function(strs) wordStem(unlist(strs), language = "porter")#Stem text
clean.review <- function(list) paste(list, collapse=' ')#Paste them together

```


##Train Word Matrix
```{r}

tokens_train <- sapply(train$text, split)
clean.tokens_train <- sapply(tokens_train, clean.tokens)
tokens.stem_train <- lapply(clean.tokens_train, tokens.stem)
clean.review_train <- lapply(tokens.stem_train, clean.review)

train$text <- clean.review_train


train_word_mat <- matrix(nrow = nrow(train), ncol = length(wordbank))
colnames(train_word_mat) <- wordbank


for (i in 1:nrow(train)) {
  train_word_mat[i,] <- apply(matrix(wordbank),1, FUN = function(x){as.double(grepl(x,train$text[i]))})
  print(paste(i, "in", nrow(train)))
}
write.csv(train_word_mat,"train_word.csv",row.names = FALSE)

train_word <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Re-try/train_word.csv") #load the matrix of text indication of train

ncol(train_word)
```


##Test Word Matrix
```{r}
tokens_test <- sapply(test$text, split)
clean.tokens_test <- sapply(tokens_test, clean.tokens)
tokens.stem_test <- lapply(clean.tokens_test, tokens.stem)
clean.review_test <- lapply(tokens.stem_test, clean.review)
test$text <- clean.review_test


test_word_mat <- matrix(nrow = nrow(test), ncol = length(wordbank))
colnames(test_word_mat) <- wordbank
for (i in 1:nrow(test)) {
  test_word_mat[i,] <- apply(matrix(wordbank),1, FUN = function(x){as.double(grepl(x,test$text[i]))})
  print(paste(i, "in", nrow(test)))
}
write.csv(test_word_mat,"test_word.csv",row.names = FALSE)
test_word <- read.csv("/Users/aitruong/Dropbox/Sp17/Stat154/Final Project/Re-try/test_word.csv") #load the matrix of text indication of test
```


##Reduce Dimensionality of Text with PCA (Train)
```{r}
train_word.pca <- prcomp(train_word, center=TRUE)

eig.val <- get_eigenvalue(train_word.pca)
text_reduced <- train
eig.val[which(eig.val$cumulative.variance.percent>95)[1],]
text.reduced_train <- train_word.pca$x[,c(1:which(eig.val$cumulative.variance.percent>95)[1])] 
dim(text.reduced_train)

```

#Date Matrix for Train
```{r}

#Split date data
train$date <- as.Date(train$date,'%Y-%m-%d')
train$year <- format(train$date,'%Y')
train$month <- month(as.POSIXlt(train$date
,format='%Y-%m-%d'))


#Divide months into seasons
train$winter <- as.double(train$month%in%c("11","12","1"))
train$spring <- as.double(train$month%in%c("2","3","4"))
train$summer <- as.double(train$month%in%c("5","6","7"))
train$fall <- as.double(train$month%in%c("8","9","10"))
train <- train[,!(names(train)%in%c("winter"))]

#Create Dummy Variable for years
inds <- unique(train$year)

year_mat <- matrix(ncol=length(unique(train$year)), nrow=length(train$year))

year.f <- factor(train$year)
year.dummies = model.matrix(~year.f)
ncol(year.dummies)
year.train <- year.dummies[,-1] 
colnames(year.train) <- c("2005","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015","2016","2017")
ncol(year.train)
```

##City Matrix for Train
```{r}
city.f <- factor(train$city)
city.dummies_train= model.matrix(~city.f)
city.train <- city.dummies_train[,-1]
ncol(city.train)
```

##Construct x and y train
```{r}
X.train.notext <- train[,!(names(train)%in%c("text","stars","date","city","year"))]

X.train <- as.matrix(cbind(text.reduced_train,
X.train.notext,year.train,city.train))

ncol(X.train)
colnames(X.train)
y.train <- train$stars 
```

##Lasso Model
```{r}
lasso_train <- cv.glmnet(x=X.train,y=y.train,alpha=1)
penalty <- lasso_train$lambda.min
lasso_train.best <- glmnet(x=X.train,y=y.train,alpha=1,lambda=penalty)

coef_lasso.best <- data.frame(as.matrix(coef(lasso_train.best)))

write.csv(coef_lasso.best,"coef_lasso.best.csv")
```

#check model
```{r}
y.pred_train <- predict(lasso_train.best,newx=X.train)
sqrt(mean((y.pred_train-y.train)^2))

```


#Date Matrix for test
```{r}

#Split date data
test$date <- as.Date(test$date,'%Y-%m-%d')
test$year <- format(test$date,'%Y')
test$month <- month(as.POSIXlt(test$date
,format='%Y-%m-%d'))


#Divide months into seasons
test$winter <- as.double(test$month%in%c("11","12","1"))
test$spring <- as.double(test$month%in%c("2","3","4"))
test$summer <- as.double(test$month%in%c("5","6","7"))
test$fall <- as.double(test$month%in%c("8","9","10"))
test <- test[,!(names(test)%in%c("winter"))]

#Create Dummy Variable for years
inds <- unique(test$year)

year_mat <- matrix(ncol=length(unique(test$year)), nrow=length(test$year))

year.f <- factor(test$year)
year.dummies = model.matrix(~year.f)
ncol(year.dummies)
year.dummies[,1] <- 0
year.test <- year.dummies 
colnames(year.test) <- c("2005","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015","2016","2017")
```

##City Matrix for Test
```{r}
city.f <- factor(test$city)
city.dummies= model.matrix(~city.f)
ncol(city.dummies)
city.test <- city.dummies[,-1]
ncol(city.test)

```

##Construct X, y Test
```{r}
PCA_test <- predict(train_word.pca, newdata=test_word)
text.reduced_test <- PCA_test[,c(1:which(eig.val$cumulative.variance.percent>95)[1])]
X.test.notext <- test[,!(names(test)%in%c("text","date","city","year"))]

X.test <- as.matrix(cbind(text.reduced_test,
X.test.notext,year.test,city.test))

```

##Check Lasso
```{r}
check <- predict(lasso_train.best, newx=X.train)
sqrt(mean((check - y.train)^2))
a <- data.frame(check, y.train)
```

##Predict Test Lasso
```{r}
y.test <- predict(lasso_train.best, newx=X.test)
length(y.test)
length(test$business_id)
predict_test <- data.frame(test.byuser$business_id,y.test)
colnames(predict_test) <- c("business_id","stars")
predict.avg_test <- aggregate(predict_test$stars, by=list(predict_test$business_id), mean)
colnames(predict.avg_test) <- c("business_id","stars")

result_test <- data.frame(predict.avg_test$business_id,predict.avg_test$stars)
colnames(result_test) <- c("business_id","stars")
write.csv(result_test, "result_test_8.csv",row.names = FALSE)
```

##Model on business only
```{r}
train_businessmod <- data.frame(train[, names(train)%in%c("stars","is_open","city","review_count.x","year","month","winter","spring","summer")])
business.mod_train <- lm(stars~.,data=train_businessmod)
summary(business.mod_train)
```







